### 2023-09-07 3.Design/activation.tex
Not so productive morning
worked on af

\begin{figure}[H]
  \centering
  \includesvg[width=\textwidth]{activation/circuit}
  \caption{Activation functions circuit}
  \label{fig:afCircuit}
\end{figure}

@@

\subsection{Symbol}
The symbol for both the sigmoid and \ac{tanh}

\begin{figure}[H]
  \centering
  \hspace*{1.5cm}
  \subfloat[Sigmoid symbol]{\includesvg[height=2.5cm]{activation/sigmoidSymbol}}%
  \hfill
  \subfloat[\ac{tanh} symbol]{\includesvg[height=2.5cm]{activation/tanhSymbol}}%
  \hspace*{1.5cm}
  \caption{Activation functions symbols}
  \label{fig:afSymbol}
\end{figure}

@@

>>>>

\begin{figure}[H]
  \centering
  \includesvg[width=\textwidth]{activation/afCircuit}
  \caption{Activation functions circuit}
  \label{fig:afCircuit}
\end{figure}

@@

\subsection{Symbols}
The symbols for the sigmoid and the \ac{tanh} are separated for better understanding.

\begin{figure}[H]
  \centering
  \hspace*{0.8cm}
  \subfloat[Sigmoid symbol]{\includesvg[height=2.5cm]{activation/sigmoidSymbol}}%
  \hfill
  \subfloat[\ac{tanh} symbol]{\includesvg[height=2.5cm]{activation/tanhSymbol}}%
  \hspace*{0.8cm}
  \caption{Activation functions symbols with the input pin on the left and the output pin on the right}
  \label{fig:afSymbol}
\end{figure}

@@

These functions are still a bit different from the original functions (especially for the \ac{tanh}). However that doesn't matter too much as the trainning will be happening within the final circuit, all weights will be set in the circuit. This is the reason why such a difference doesn't matter. As long as the curves have the similar shape, the result won't be drastically affected.
